Learning constraints in tabular data

### 2016-05-26 Paper/ECAI/tabular.tex
reworked sec2 part about redundancy

\newcommand{\eccalc}[2]{\ensuremath{#1 = #2}}
\newcommand{\ecrank}[2]{\eccalc{#1}{\textit{RANK}(#2)}}
\newcommand{\ecfkey}[2]{\ensuremath{\textit{FOREIGNKEY}(#1,#2)}}
\newcommand{\ecalldiff}[1]{\ensuremath{\textit{ALLDIFFERENT}(#1)}}
\newcommand{\eclookupf}[4]{\ensuremath{\textit{LOOKUP}_{\textit{#4}}(#1, #2, #3)}}
\newcommand{\eclookup}[4]{\eccalc{#1}{\eclookupf{#2}{#3}{#4}{}}}
\newcommand{\eclookupprod}[5]{\eccalc{#1}{#2 \times \eclookupf{#3}{#4}{#5}{}}}
\newcommand{\eclookupfuzzy}[4]{\eccalc{#1}{\eclookupf{#2}{#3}{#4}{fuzzy}}}
\newcommand{\ecperm}[1]{\ensuremath{\textit{PERMUTATION}(#1)}}
\newcommand{\ecseries}[1]{\ensuremath{\textit{SERIES}(#1)}}
\newcommand{\ecprod}[3]{\eccalc{#1}{#2 \times #3}}
\newcommand{\ecdiff}[3]{\eccalc{#1}{#2 - #3}}
\newcommand{\ectotal}[3]{\eccalc{#1}{\textit{PREV}(#1) + #2 - #3}}
\newcommand{\ecproj}[2]{\eccalc{#1}{\textit{PROJECT}(#2)}}
\newcommand{\ecaggc}[3]{\eccalc{#2}{\textit{#1\textsubscript{col}}(#3)}}
\newcommand{\ecaggr}[3]{\eccalc{#2}{\textit{#1\textsubscript{row}}(#3)}}
\newcommand{\ecsumc}[2]{\eccalc{#1}{\textit{SUM\textsubscript{col}}(#2)}}
\newcommand{\ecsumr}[2]{\eccalc{#1}{\textit{SUM\textsubscript{row}}(#2)}}
\newcommand{\ecaggif}[5]{\eccalc{#2}{\textit{#1IF}(#3, #4, #5)}}
\newcommand{\ecsumif}[4]{\eccalc{#1}{\textit{SUMIF}(#2, #3, #4)}}
\newcommand{\ecsumprod}[3]{\eccalc{#1}{\textit{SUMPRODUCT}(#2, #3)}}

@@

\tias{This should contain examples that recur later in the text}

For example, for some constraints, the order of some of the arguments may not matter. For example for the product constraint, $\ecprod{\sg_r}{\sg_1}{\sg_2} \equiv \ecprod{\sg_r}{\sg_2}{\sg_1}$ so one can be considered redundant to the other.

\samuel{Should this not be part of approach / optimizations / redundancy?}One way to deal with such equivalences is to identify a \textit{canonical} constraint among the equivalent ones. For example, for the product constraint above, we could define a lexicographic ordering over the blocks and only consider the constraint with the smallest ordering.

Because dealing with redundancy is often application-dependent, we explain in the next section our generic method for finding all constraints.

@@

\subsection{Optimizations}
This section discusses various essential design decisions and optimizations aiming to improve the speed and extensibility of our system as well as to find less redundant constraints.

>>>>

\newcommand{\eccalc}[2]{\ensuremath{#1 = #2}}
\newcommand{\ecrank}[2]{\eccalc{#1}{\textit{RANK}(#2)}}
\newcommand{\ecfkey}[2]{\ensuremath{\textit{FOREIGNKEY}(#1,#2)}}
\newcommand{\ecalldiff}[1]{\ensuremath{\textit{ALLDIFFERENT}(#1)}}
\newcommand{\eclookupf}[4]{\ensuremath{\textit{LOOKUP}_{\textit{#4}}(#1, #2, #3)}}
\newcommand{\eclookup}[4]{\eccalc{#1}{\eclookupf{#2}{#3}{#4}{}}}
\newcommand{\eclookupprod}[5]{\eccalc{#1}{#2 \times \eclookupf{#3}{#4}{#5}{}}}
\newcommand{\eclookupfuzzy}[4]{\eccalc{#1}{\eclookupf{#2}{#3}{#4}{fuzzy}}}
\newcommand{\ecperm}[1]{\ensuremath{\textit{PERMUTATION}(#1)}}
\newcommand{\ecseries}[1]{\ensuremath{\textit{SERIES}(#1)}}
\newcommand{\ecprod}[3]{\eccalc{#1}{#2 \times #3}}
\newcommand{\ecdiv}[3]{\eccalc{#1}{{#2} / {#3}}}
\newcommand{\ecdiff}[3]{\eccalc{#1}{#2 - #3}}
\newcommand{\ectotal}[3]{\eccalc{#1}{\textit{PREV}(#1) + #2 - #3}}
\newcommand{\ecproj}[2]{\eccalc{#1}{\textit{PROJECT}(#2)}}
\newcommand{\ecaggc}[3]{\eccalc{#2}{\textit{#1\textsubscript{col}}(#3)}}
\newcommand{\ecaggr}[3]{\eccalc{#2}{\textit{#1\textsubscript{row}}(#3)}}
\newcommand{\ecsumc}[2]{\eccalc{#1}{\textit{SUM\textsubscript{col}}(#2)}}
\newcommand{\ecsumr}[2]{\eccalc{#1}{\textit{SUM\textsubscript{row}}(#2)}}
\newcommand{\ecaggif}[5]{\eccalc{#2}{\textit{#1IF}(#3, #4, #5)}}
\newcommand{\ecsumif}[4]{\eccalc{#1}{\textit{SUMIF}(#2, #3, #4)}}
\newcommand{\ecsumprod}[3]{\eccalc{#1}{\textit{SUMPRODUCT}(#2, #3)}}

@@

Within the same constraint, there can be equivalent argument assignments if the order of some of the arguments does not matter. For example for the product constraint, $\ecprod{\sg_r}{\sg_1}{\sg_2} \equiv \ecprod{\sg_r}{\sg_2}{\sg_1}$ so one can be considered redundant to the other.

Two different constraints may be logically equivalent due to their nature, e.g. for addition/subtraction and product/division: $\ecprod{\sg_r}{\sg_1}{\sg_2} \equiv \ecdiv{\sg_1}{\sg_r}{\sg_2}$.

When the data has rows or columns containing exactly the same data, then any constraint with such a vector in its argument assignment will also have an argument assignment with the other equivalent vectors.

Because dealing with redundancy is often application-dependent, we explain in the next section our generic method for finding all constraints. We describe some optimisations that avoid obvious equivalences in Section~\ref{sec:opts} and will investigate the impact of redundancy in the experiments.

@@

\subsection{Optimizations} \label{sec:opts}
\samuel{Should this not be part of approach / optimizations / redundancy?}One way to deal with such equivalences is to identify a \textit{canonical} constraint among the equivalent ones. For example, for the product constraint above, we could define a lexicographic ordering over the blocks and only consider the constraint with the smallest ordering.

This section discusses various essential design decisions and optimizations aiming to improve the speed and extensibility of our system as well as to find less redundant constraints.
